On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-04-08 manuscripts/PNAS/chazthm_pnas.tex
typo

\begin{lemma}\label{NonEmptyLemma} 
Fix $\ell, m$, and $\bar m$. Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular with the SIP.  If $\pi: E \to 2^{[\bar m]}$ has $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
\begin{align}\label{cond}
|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |,\ \ \   \text{for } F \subseteq E,
\end{align}
then $\bar m \geq m$ and the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $J$ to $[\bar m]$ for some $J \subseteq [m]$ of size $\bar m - \ell(\bar m - m)$. In particular, if $\bar m = m$ then the map $\pi$ is induced by a permutation.
\end{lemma}

>>>>

\begin{lemma}\label{NonEmptyLemma} 
Fix $\ell, m$, and $\bar m$. Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular with the SIP.  If $\pi: E \to 2^{[\bar m]}$ has $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
\begin{align}\label{cond}
|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |,\ \ \   \text{for } F \subseteq E,
\end{align}
then $\bar m \geq m$ and the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $J$ to $[\bar m]$ for some $J \subseteq [m]$ of size $p = \bar m - \ell(\bar m - m)$. In particular, if $\bar m = m$ then the map $\pi$ is induced by a permutation.
\end{lemma}
